\chapter*{Acknowledges}
%\addcontentsline{toc}{chapter}{Agradecimentos}

I would like to express my heartfelt gratitude and appreciation to several individuals who have played a significant role in the completion of this report.\newline

Firstly, I would like to extend my sincere thanks to my academic supervisor, Luís Ferreira, for his guidance, support and valuable feedback throughout the entire process. His expertise and insights have been instrumental in shaping this report and enhancing its quality. I am truly grateful for his time, dedication and commitment to my academic and professional growth.\newline

I would also like to acknowledge my internship supervisor, Emanuel Mota, for his constant encouragement, support and understanding during this journey. His guidance and mentorship has been invaluable and I am grateful for the opportunities and experiences I have gained under his supervision. His belief in my abilities has been a tremendous source of motivation. Along with Emanuel, I would like to thank Yarilabs team and congratulate them for their amazing work, especially Susana, for being a female role model throughout the entire process and that I will definitely cherish throughout my entire life; Pedro Costa, for being incredibly intelligent and efficient, giving me an example of whom I'm trying to be as a developer; João Martins, for sticking with me during the primordial times of the internship; and Victor Le Pen, Marlene, Hélder Pinto, Tiago Bouças and many others, whom I've had the pleasure to dive deeper into their amazing personalities and programming skills. Maggie, the office dog, was also a cloud-shaped friend that I will always thank for napping next to me while I was working.\newline

Lastly, I would like to express my deepest appreciation to my family, especially Maria Noversa, Andreia Lima, Bárbara Silva and Nuno Maia, for their unwavering love, encouragement and understanding throughout my academic pursuits. Their continuous support and belief in my abilities have been the cornerstone of my success. I am forever grateful for their sacrifices, patience, and encouragement during both the highs and lows of this endeavor.\newline

I am honored to have had the opportunity to work with such remarkable individuals who have contributed significantly to my personal and professional development. Thank you once again for your unwavering support, guidance and belief in my abilities.

\vspace{10mm}
\flushleft{Bruna Macieira}
