\chapter*{Abstract}
%\addcontentsline{toc}{chapter}{Abstract}

% Keywords command
\providecommand{\keywords}[1]
{
  \small	
  \textbf{\textit{Keywords---}} #1
}


The adoption of decentralized finance (DeFi) services has emerged as a groundbreaking paradigm, revolutionizing the traditional financial landscape and holds promise for creating a more equitable economic world. In this report, we explore the remarkable innovation and transformative potential of Dharma Network, a pioneering decentralized application built on the Algorand blockchain.\newline

Global income inequality has long been a pressing issue, with the wealth gap between the rich and the poor widening over time. Traditional financial systems, characterized by centralized control and exclusionary practices, have played a role in perpetuating this inequality. Many individuals and communities, particularly those in low-income areas, face barriers such as limited access to banking services, high transaction fees, and a lack of financial opportunities.\newline

DeFi has garnered significant attention in recent years, offering individuals access to a wide array of financial services and instruments, all facilitated through smart contracts and blockchain technology. Dharma Network stands out as a prominent player in this rapidly evolving ecosystem, providing users with a seamless and secure platform to engage in decentralized lending and borrowing. Moreover, Dharma Network ensures inclusivity by giving equal representation and democratic participation to all individuals, particularly those from underserved communities.\newline

The open and permissionless nature of Dharma Network fosters financial universality, enabling anyone with an Internet connection to access and benefit from its services. Unlike traditional financial institutions that often impose barriers and exclude certain individuals, Dharma Network embraces a borderless approach, empowering users from all corners of the globe to participate in the new decentralized economy.\newline

As DeFi gains traction globally and continues to disrupt the financial sector, Dharma Network stands as a shining example of how blockchain technology can reshape the financial landscape, ushering in a new era of acceptance, accessibility, diversity and financial and democratic freedom.


\vspace*{2cm}

\keywords{Decentralized finance, Dharma Network, blockchain, Algorand, inequality, permissionless, democratic participation} 



